Dominance Regions for Rank Two Cluster Algebras

### 2022-06-09 dominance_regions.tex
,

\author{Dylan Rupel}
\author{Salvatore Stella}
\address[D. Rupel]{\href{mailto:rupel.dylan@pusd.us}{\textup{\texttt{rupel.dylan@pusd.us}}}  Math Academy, Pasadena Unified School District, Pasadena, CA 91109 USA}
\address[S. Stella]{\href{mailto:salvatore.stella@univaq.it}{\textup{\texttt{salvatore.stella@univaq.it}}}, Dipartimento di Ingegneria e Scienze dell'Informazione e Matematica, Università degli Studi dell'Aquila, IT}
%\email[Salvatore Stella]{stella@math.haifa.ac.il}
%\keywords{}
\thanks{Salvatore Stella was partially supported by the University of Leicester and the University of Rome ``La Sapienza''.}
%\thanks{Nathan Reading was partially supported by the National Science Foundation under Grant Numbers DMS-1500949 and DMS-2054489 and by the Simons Foundation under award number 581608.\\
%\indent Salvatore Stella was partially supported by ISF grant \#1144/16, the University of Haifa, the University of Leicester, and the University of Rome ``La Sapienza''.}

>>>>

\author{Dylan Rupel}
\author{Salvatore Stella}
\address[D. Rupel]{\href{mailto:rupel.dylan@pusd.us}{\textup{\texttt{rupel.dylan@pusd.us}}}, Math Academy, Pasadena Unified School District, Pasadena, CA 91109 USA}
\address[S. Stella]{\href{mailto:salvatore.stella@univaq.it}{\textup{\texttt{salvatore.stella@univaq.it}}}, Dipartimento di Ingegneria e Scienze dell'Informazione e Matematica, Università degli Studi dell'Aquila, IT}
%\email[Salvatore Stella]{stella@math.haifa.ac.il}
%\keywords{}
\thanks{Salvatore Stella was partially supported by the University of Leicester and the University of Rome ``La Sapienza''.}
%\thanks{Nathan Reading was partially supported by the National Science Foundation under Grant Numbers DMS-1500949 and DMS-2054489 and by the Simons Foundation under award number 581608.\\
%\indent Salvatore Stella was partially supported by ISF grant \#1144/16, the University of Haifa, the University of Leicester, and the University of Rome ``La Sapienza''.}
